GPU-friendly Stroke Expansion

### 2024-06-14 paper.tex
Add question-mark figure

\begin{figure}
    \includegraphics[scale=0.24]{cusp_rendering}
    \caption{Rendering of a cubic Bézier cusp using Euler spiral segments}
    \Description{A cubic Bézier with a cusp is approximated by Euler spiral segments with finite curvature, including one with a question mark shape. The resulting stroke outlines have the correct shape.}
    \label{fig:cusp_rendering}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[scale=0.5]{question}
    \caption{Subdivision of a cubic Bézier with a cusp into continuous Euler spiral segments.}
    \Description{A cubic Bézier with a cusp is approximated by Euler spiral segments with finite curvature, including one with a question mark shape.}
    \label{fig:cusp_rendering}
\end{figure}
